Verifying Demonstrations

### 2017-08-08 intro.tex
Adds another comment about Venezuela
Minor edit to intro about governments organizing protests

We can make one important observation about this problem that has seemingly 
been ignored in the past: it is an adversarial setting.
The protesters (organizers and participants) have an incentive to increase the 
tallied number of participants, whereas other interests might have an incentive 
to decrease the tallied number of participants, e.g.\ an authoritarian regime.
(Or the other way around, an authoritarian regime wants to organize a 
pro-regime protest to demonstrate its \enquote{wide support}.)
To solve this problem, we need a verifiable participation count.
In this paper, we combine the verifiability and privacy properties of 
electronic voting with location-proof systems to provide a verifiable 
participation count.

>>>>

We can make one important observation about this problem that has seemingly 
been ignored in the past: it is an adversarial setting.
The protesters (organizers and participants) have an incentive to increase the 
tallied number of participants, whereas other interests might have an incentive 
to decrease the tallied number of participants, e.g.\ an authoritarian regime.
Or the other way around, sometimes an authoritarian regime wants to organize a 
pro-regime protest to demonstrate its \enquote{wide support}.
% XXX Wasn't this the case in Venezuela?
(This makes it difficult to rely on government-issued credentials to prevent a 
Sybil attack --- government can issue arbitrarily many such credentials for its 
own protests.)
To solve this problem, we need a verifiable participation count which is 
protected from Sybil attacks.
In this paper, we combine the verifiability and privacy properties of 
electronic voting with location-proof systems to provide a verifiable 
participation count.
